---
title: "MEDS Week 3 Recap"
description: |
  A brief look at some of the concepts we've learned so far.
author:
  - name: Alex Clippinger
    url: {}
date: 08-16-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: Toggle Code
preview: images/logo-bren.svg
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

We are in week 3 of the MEDS program at UCSB's Bren School of Environmental Science and Management. Here are a few things that we've learned...

#### R functions:

So far, we have learned various methods of getting data into more usable formats.

Here is an example of using the dplyr `group_by` and `summarize` functions...

```{r, include = TRUE}
# Example using the palmerpenguins dataset
penguins_summary <- penguins %>% 
  group_by(species) %>% 
  summarize(mean_body_mass_g = mean(body_mass_g, na.rm = TRUE))

penguins_summary
```

#### Concepts

We have also learned fundamental concepts for working with data. One such concept is **tidy data**, which refers to the following qualities:
- Each column contains a single variable
- Each row contains a single observation
- Each cell contains a single value

This is important for other important concepts that we've learned, such as scientific reproducibility.

#### Takeaways
The MEDS program has been rewarding and challenging in the initial weeks. I have learned to think critically and deliberately about every bit of code that I write. I have also appreciated the helpful and collaborative community that has formed in our small cohort.
